Software Citation Principles

### 2016-05-09 sc-principles/software-citation-principles.tex
add library to stakeholders of mixed packages
It's a use case that is very relevant to all data archives and one that
I'm trying to figure out how to best handle

17.\ Publish mixed data\slash software packages  & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textopenbullet & \textopenbullet & \textopenbullet & Repository \\

>>>>

17.\ Publish mixed data\slash software packages  & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textopenbullet & \textopenbullet & \textopenbullet & Repository, library, archive \\
